---
title: "DiD TWFE-Q"
author: "Hans Martinez"
date: '`r format(Sys.time(),"%d %b, %Y")`'
output: 
  pdf_document:
    extra_dependencies: tabularx, booktabs, footnote, bbm, bm
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("DID_twfe_q.Rdata")
library(fixest)
myD= c("retail_p_gas"="Gas retail price",
       "retail_p_eth"="Ethanol retail price",
       "ws_p_gas"="Gas wholesale price",
       "ws_p_eth"="Ethanol wholesale price",
       "No_st_total"="Total number of stations",
       "Dist_No_main"="Number of main distributors",
       "Dist_No_other"="Number of other distributors",
       "Ind_st_sh"="Share of independent stations",
       "Vol_tot"="Total volume",
       "Vol_gas"="Gas volume",
       "Vol_eth"="Ethanol volume",
       "Vol_dies"="Diesel volume",
       "Fleet_tot"="Total fleet",
       "population"="Population",
       "gdp_pc"="GDP per capita",
       "hhi"="HHI",
       "merge"="Merge",
       "group::Both"="Both",
       "group::Just_one"="Just one",
       "log(retail_p_gas)"="$ln$(Gas retail price)",
       "log(retail_p_eth)"="$ln$(Ethanol retail price)",
       "log(ws_p_gas)"="$ln$(Gas wholesale price)",
       "log(ws_p_eth)"="$ln$(Ethanol wholesale price)",
       "mun"="Municipality",
       "month"="Month-Year",
       "qt"="Quarter",
       "log(Vol_tot)"="$ln$(Total volume)",
       "log(Vol_gas)"="$ln$(Gas volume)",
       "log(Vol_eth)"="$ln$(Ethanol volume)",
       "log(Vol_dies)"="$ln$(Diesel volume)",
       "log(No_st_total)"="$ln$(Total number of stations)",
       "log(No_st_Unbranded)"="$ln$(Number of independent stations)")
```

# Diff-in-Diff two way fixed effects (TWFE)

\begin{equation}
  Y_{it}=\bm{\beta'}_{t}(Treatment_{it}*\bm{Month}_{t}) + \alpha X_{it} + \gamma^{Mun}_{i} + \gamma^{Qt}_{t}  + \varepsilon_{it}
\end{equation}

where $i$ stands for municipality and $t$ for month. $Y_{it}$ is one of the outcome variables of interest. $Treatment_{it}$ is a dummy variable equal to one if the municipality is in the treatment group and zero if it is in the control group. $Month_{t}$ is a vector of the month-year period dummy variables (96 month-year periods). $\gamma^{Mun}_{i}$ and $\gamma^{Qt}_{t}$ are municipality and month-year fixed effects, respectively. Finally, $X_{it}$ is a vector of control variables.

The graphs below show only the interaction between the *Month* and the *Treatment* variables.

# Both as treatment, Just One and None as control

```{r did_twfe, results='asis', echo=FALSE}

for (i in 1:length(did_twfe_q_b)){
  iplot(did_twfe_q_b[[i]])
}
rm(did_twfe_q_b)
```

# Both as treatment, None as control

```{r did_twfe_q_bn, results='asis', echo=FALSE}
for (i in 1:length(did_twfe_q_bn)){
  iplot(did_twfe_q_bn[[i]])
}
rm(did_twfe_q_bn)
```

# Just One as treatment, None as control

```{r did_twfe_q_jn, results='asis', echo=FALSE}

for (i in 1:length(did_twfe_q_jn)){
  iplot(did_twfe_q_jn[[i]])
}
rm(did_twfe_q_jn)
```
