---
title: "DiD-Placebo"
author: "Hans Martinez"
date: '`r format(Sys.time(),"%d %b, %Y")`'
output: 
  pdf_document:
    extra_dependencies: tabularx, booktabs, footnote, bbm
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("DID_pbo.Rdata")
library(fixest)
myD= c("retail_p_gas"="Gas retail price",
       "retail_p_eth"="Ethanol retail price",
       "ws_p_gas"="Gas wholesale price",
       "ws_p_eth"="Ethanol wholesale price",
       "No_st_total"="Total number of stations",
       "Dist_No_main"="Number of main distributors",
       "Dist_No_other"="Number of other distributors",
       "Ind_st_sh"="Share of independent stations",
       "Vol_tot"="Total volume",
       "Vol_gas"="Gas volume",
       "Vol_eth"="Ethanol volume",
       "Vol_dies"="Diesel volume",
       "Fleet_tot"="Total fleet",
       "population"="Population",
       "gdp_pc"="GDP per capita",
       "hhi"="HHI",
       "merge"="Merge",
       "group::Both"="Both",
       "group::Just_one"="Just one",
       "log(retail_p_gas)"="$ln$(Gas retail price)",
       "log(retail_p_eth)"="$ln$(Ethanol retail price)",
       "log(ws_p_gas)"="$ln$(Gas wholesale price)",
       "log(ws_p_eth)"="$ln$(Ethanol wholesale price)",
       "mun"="Municipality",
       "month"="Month-Year",
       "qt"="Quarter",
       "placebo"="Placebo",
        "log(Vol_tot)"="$ln$(Total volume)",
       "log(Vol_gas)"="$ln$(Gas volume)",
       "log(Vol_eth)"="$ln$(Ethanol volume)",
       "log(Vol_dies)"="$ln$(Diesel volume)",
       "log(No_st_total)"="$ln$(Total number of stations)",
       "log(No_st_Unbranded)"="$ln$(Number of independent stations)")
```

# Diff-in-Diff Placebo

\begin{equation}
  Y_{it}=\beta_{0}(Treatment_{it}*Placebo_{it}) + \beta_1 X_{it} + \alpha_{i} + \gamma_{t}  + \varepsilon_{it}
\end{equation}

where $i$ stands for municipality and $t$ for month. $Y_{it}$ is one of the outcome variables of interest. $Treatment_{it}$ is a dummy variable equal to one if the municipality is in the treatment group and zero if it is in the control group. Likewise, $Placebo_{it}$ is a dummy variable that is equal to one if the month is greater than November 2010, the **fake** date of the merge between Shell and Cosan. $\alpha_i$ and $\gamma_t$ are municipality and month-year fixed effects, respectively. Finally, $X_{it}$ is a vector of control variables.

Sample is restricted until the date of the merger.

### Both as treatment, Just One and None as control

```{r did, results='asis', echo=FALSE}
for (i in seq(1,length(did_pbo_b),by=5)){
  etable(did_pbo_b[i:(i+4)], tex = T, dict = myD)
  cat("\n")
}
```

# Both as treatment, None as control

```{r did_pbo_bn, results='asis', echo=FALSE}
for (i in seq(1,length(did_pbo_bn),by=5)){
  etable(did_pbo_bn[i:(i+4)], tex = T, dict = myD)
  cat("\n")
}
```

# Just One as treatment, None as control

```{r did_pbo_jn, results='asis', echo=FALSE}
for (i in seq(1,length(did_pbo_b),by=5)){
  etable(did_pbo_jn[i:(i+4)], tex = T, dict = myD)
  cat("\n")
}
```
